Letter to the Editor

### 2023-02-23 editorial-communication/cover-letter-submission.Qmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@6500cdf1e50df11f876d0a05b756c5722fc4e223 🚀

---
title: Letter to the Editor
subtitle: "Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution"
date: today
date-format: long
format:
  html:
    theme: cosmo 
    highlight-style: tango
    embed-resources: true
---
```{r include=FALSE}
knitr::opts_chunk$set(fig.retina = 2)
```

>>>>

---
title: Letter to the Editor
subtitle: "Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution"
date: today
date-format: long
format:
  html:
    theme: cosmo 
    highlight-style: tango
    embed-resources: true
---
